linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity

### 2021-09-08 code/linguistic_analysis_C-D.Rmd
update rmd with figs and new format utilities data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(here)
library("stringr")
library(Hmisc)
library("spacyr")
library(ggrepel)

@@

```{r main data, include=TRUE}
d<- read_csv("../data/processed_data/joined_data/filtered_raw_chat.csv")
d_flowers <- d %>% 
  filter(type=="message") %>%
  filter(!is.na(text)) %>% 
  filter(!conditionName=="coopCartel")

write_csv(d, "../data/processed_data/raw_chat3.csv")

d_flowers <- d_flowers %>% 
  filter(!conditionName=="coopCartel")

@@

### 1. Utt Length
```{r utt_length}

@@

#, color=as.factor(gameId)

#jpeg("~/Desktop/plots/nwords_block.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_block, aes(x=blockNum, y=total_num_words, color=condition))+
  #facet_grid(rows =vars(condition)) +
  geom_point()+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Total number of words", x="Block number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("Number of words per block")#+
 # theme(text = element_text(size = 30))
#color="gameId" cols = vars(blockNum),
#dev.off()

@@

#jpeg("~/Desktop/plots/nwords_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=total_num_words,  color=condition))+
#  facet_grid(rows =vars(condition)) +
  geom_point()+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Total number of words", x="Trial number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("Number of words per trial")#+
#  theme(text = element_text(size = 30))
#dev.off()

#jpeg("~/Desktop/plots/mlu_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=mlu,  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="Mean Length of Utterance", y="MLU", x="Trial number")+
  theme_jmank() + scale_color_bay() + theme(legend.position="bottom") #+ 
  #theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nword_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_rep, aes(x=repNum, y=total_num_words,  color=condition))+
#  facet_grid(rows =vars(condition)) +
  geom_point()+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Total number of words", x="Rep number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("Number of words per rep")#+
#  theme(text = element_text(size = 30))
#dev.off()

#jpeg("~/Desktop/plots/mlu_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_rep, aes(x=repNum, y=mlu,  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Rep number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("MLU per rep")#+
 # theme(text = element_text(size = 30))
#dev.off()

ggplot(d_flowers_utt_length_rep, aes(x=repNum, y=log(mlu+1),  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Rep number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("MLU per rep")#+
 # theme(text = element_text(size = 30))
#dev.off() 
```

### 2. Number of turns
```{r number_of_turns}

d_flowers_n_turns_rep <- d_flowers %>%
  group_by(gameId, condition, repNum)  %>%
  summarise(n=n())

#jpeg("~/Desktop/plots/nturn_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_n_turns_rep, aes(x=repNum, y=n,  color=condition))+
 # facet_grid(rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Rep number")+
  theme(legend.position="bottom") + 
  theme_bw() +
  ggtitle("Number of turns per Rep")#+
#  theme(text = element_text(size = 30))
#dev.off()

@@

ggsave("../figs/num_turns_block.png", height = 3, width = 3)
```

#second plot
### 2b. Number of turns

@@

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by( repNum, gameId, condition) %>%
  summarise(n_utt_speaker=n())

#jpeg("~/Desktop/plots/nutts_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_n_utt_speaker, 
       aes(x=repNum, y=n_utt_speaker,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
#  facet_grid(~condition) +
  xlab("Rep number") + 
  ylab("Number of utterances") + 
  theme_bw()#+
#  theme(text = element_text(size = 30))
#dev.off()

@@

### 3. Parts of speech
```{r pos, eval=FALSE, include=FALSE}

# text <- d_flowers$text
# parsed <- spacy_parse(text,pos=TRUE) %>%
#   select(doc_id, pos) %>%
#   group_by(doc_id) %>%
#   mutate(pos = paste(pos, collapse=",")) %>%
#   distinct()
#   
# d_flowers_pos  <- cbind(d_flowers, parsed) %>%
#   separate_rows(pos, convert = TRUE) %>%
#   group_by(condition, blockNum, gameId, pos) %>%
#   filter(pos=="NOUN"| pos=="VERB" | pos=="ADJ"| pos=="ADP"| pos=="DET" | pos=="PRON") %>%
#   summarise(pos_count=n()) %>%
#   left_join(d_flowers_utt_length_block) %>%
#   mutate(prop_pos=pos_count/total_num_words)
#         
# #jpeg("~/Desktop/plots/pos_block.jpg", width = 950, height = 950)
# ggplot(d_flowers_pos, 
#        aes(x=blockNum, y=prop_pos, label=gameId,  color=condition)) + 
#   geom_smooth(method = "lm", formula = y~x) + 
#   geom_point(alpha=.1) +
#   facet_grid( cols=vars(pos)) +
#   xlab("Block number") + 
#   ylab("Proportion of pos") + 
#   theme_bw()#+
#  # theme(text = element_text(size = 30))
# #dev.off() 
# 
# d_flowers_pos  <- cbind(d_flowers, parsed) %>%
#   separate_rows(pos, convert = TRUE) %>%
#   group_by(condition, trialNum, gameId, pos) %>%
#   filter(pos=="NOUN"| pos=="VERB" | pos=="ADJ"| pos=="ADP"| pos=="DET" | pos=="PRON") %>%
#   summarise(pos_count=n()) %>%
#   left_join(d_flowers_utt_length_trial) %>%
#   mutate(prop_pos=pos_count/total_num_words)
#         
# #jpeg("~/Desktop/plots/pos_trial.jpg", width = 950, height = 950)
# ggplot(d_flowers_pos, 
#        aes(x=trialNum, y=prop_pos, label=gameId,  color=condition)) + 
#   geom_smooth(method = "lm", formula = y~x) + 
#   geom_point(alpha=.1) +
#   facet_grid( cols=vars(pos)) +
#   xlab("Trial number") + 
#   ylab("Proportion of pos") + 
#   ylim(0,5)+
#   theme_bw()#+
#   #theme(text = element_text(size = 30))
# #dev.off() 
# 
# d_flowers_pos  <- cbind(d_flowers, parsed) %>%
#   separate_rows(pos, convert = TRUE) %>%
#   group_by(condition, repNum, gameId, pos) %>%
#   filter(pos=="NOUN"| pos=="VERB" | pos=="ADJ"| pos=="ADP"| pos=="DET" | pos=="PRON") %>%
#   summarise(pos_count=n()) %>%
#   left_join(d_flowers_utt_length_rep) %>%
#   mutate(prop_pos=pos_count/total_num_words)
#         
# #jpeg("~/Desktop/plots/pos_rep.jpg", width = 950, height = 950)
# ggplot(d_flowers_pos, 
#        aes(x=repNum, y=prop_pos, label=gameId, color=condition)) + 
#   geom_smooth(method = "lm", formula = y~x) + 
#   geom_point(alpha=.1) +
#   facet_grid(cols=vars(pos)) +
#   xlab("Rep number") + 
#   ylab("Proportion of pos") +
#   ylim(0,5)+
#   theme_bw()#+
#  # theme(text = element_text(size = 30))
# #dev.off() 
```

### 4. Lexical Diversity (TTR)

@@

d_flowers_text_rep <- d_flowers %>%
    group_by(gameId, repNum, condition) %>%
    mutate(text_block = paste0(text, collapse = " ")) %>%
    select(-c(text)) %>%
    distinct()

d_flowers_ttr_rep <- d_flowers_text_rep %>%
  mutate(ttr_ = ttr(text_block))

#jpeg("~/Desktop/plots/ttr_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_ttr_rep, 
       aes(x=repNum, y=ttr_,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
 # facet_grid(rows =vars(condition)) +
  xlab("Rep number") + 
  ylab("Type_token ratio") + 
  ylim(0,1)+
  theme_bw()+
  ggtitle("TTR per rep")#+
 # theme(text = element_text(size = 30))
#dev.off()

@@

## STEP FOUR - Feedback items and markers
### 1. Distribution of speech across speakers
```{r word_length}

@@

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(playerId, repNum, gameId, condition) %>%
  summarise(n_utt_speaker=n())

d_flowers_n_utt_game <- d_flowers %>%
  group_by(repNum, gameId, condition) %>%
  summarise(n_utt_game=n())

@@

#jpeg("~/Desktop/plots/proputts_rep_speaker.jpg", width = 950, height = 950)
ggplot(d_flowers_n_utt_dist, 
       aes(x=repNum, y=overall_turns, label=playerId,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
 # facet_wrap(~condition)+
  xlab("Rep number") + 
  ylab("Proportion of turns") + 
  theme_bw()+
  ggtitle("Proportion of turns per rep and speaker")#+
 # theme(text = element_text(size = 30))
#dev.off()

@@

### 2. Turn-eliciting questions

@@

#####

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(repNum, gameId, condition) %>%
  summarise(n_utt_speaker=n())

d_flowers_q <- d_flowers %>% 
 mutate(sentence_type = ifelse(str_detect(text, "\\?"), 
                             "question",
                             "other")) %>%
 group_by(repNum, gameId, sentence_type) %>%
 summarise(n_sentence_Type=n()) %>%
 filter(sentence_type=="question") %>%
 left_join(d_flowers_n_utt_speaker) %>%
 mutate(prop_questions = n_sentence_Type/n_utt_speaker )

#jpeg("~/Desktop/plots/propquestions_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_q, 
       aes(x=repNum, y=prop_questions, label=gameId,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
#  facet_wrap(~ condition) +
  geom_point(alpha=.5) +
  xlab("Rep number") + 
  ylab("Proportion of questions") + 
  theme_bw()+
  ggtitle("Proportion of questions per rep")#+
#theme(text = element_text(size = 30))
#dev.off()

@@

### 1. Distribution of speech across speakers
```{r feedback}

###politeness markers

###backchanneling: (https://www.reading.ac.uk/AcaDepts/ll/app_ling/internal/Cutrone_vol_2.pdf)

backchanneling<- c("mm", "okay", "uh-huh", "ok", "mm-hm", "uh", "um", "agree", "uhuh", "mmm", "wow", "great", "mm", "hm",  "ummm", "hmmmm", "huh", "un", "um", "ohh", "ooo", "see", "oooo", "ununun", "oh", "ah", "true", "agree", "right", "yeah", "good", "really")

###hedges: (https://www.researchgate.net/publication/280125979_Linguistic_Markers_and_Stylistic_Attributes_of_Hedging_in_English_Academic_Papers_Written_by_Native_and_Non-Native_Speakers_of_English/figures)

hedging <- c("may", "perhaps", "might", "possible", "likely", "possibly", "maybe", "probable", "appear", "seem", "suggest", "sometimes", "seemingly", "apparently", "often", "could", "usually", "likely", "tend", "sometimes", "probably", "primarily", "tendency", "largely")

@@

d_flowers_feedback<- d_flowers %>%
  group_by(repNum, gameId, condition) %>%
  mutate(text = gsub('[[:punct:] ]+',' ',text)) %>%          
  mutate(text = strsplit(text, " ")) %>%
  rowwise() %>%
  mutate(backchannel=list(intersect(backchanneling, text))) %>%
  mutate(backchannel_length=length(backchannel))%>%
  mutate(hedge=list(intersect(hedging, text))) %>%
  mutate(hedge_length=length(hedge)) %>%
  group_by(gameId, repNum, condition)  %>%
  summarise(total_num_backchannel = sum(backchannel_length),
            total_num_hedge = sum(hedge_length)) %>%
  left_join(d_flowers_nwords) %>%
  mutate(prop_backchannel_words= total_num_backchannel/total_num_words) %>%
  mutate(prop_hedge_words= total_num_hedge/total_num_words)

#jpeg("~/Desktop/plots/propbackchannel_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_feedback, aes(y=prop_backchannel_words , x=repNum, label=gameId,  color=condition)) +
  #facet_wrap(~ condition) +
  geom_point(alpha = .5)+
  geom_smooth()+
  xlab("Rep number") + 
  ylab("Proportion of backchannel words") + 
  theme_bw()+
  ggtitle("Proportion of backchannel words per rep")#+
 # theme(text = element_text(size = 30))
#dev.off()

#jpeg("~/Desktop/plots/prophedge_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_feedback, aes(y=prop_hedge_words , x=repNum, label=gameId,  color=condition)) +
#  facet_wrap(~ condition) +
  geom_point(alpha = .5)+
  geom_smooth()+
  xlab("Rep number") + 
  ylab("Proportion of hedge words") + 
  theme_bw()+
  ggtitle("Proportion of hedge words per rep")#+
  #theme(text = element_text(size = 30))
#dev.off()

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(here)
library("stringr")
library(Hmisc)
library("spacyr")
library(ggrepel)
library(cowplot)
library(grid)
library(gridExtra)

@@

```{r main data, include=TRUE}
d<- read_csv("../data/processed_data/joined_data/filtered_raw_chat.csv")
d_flowers <- d %>% 
  filter(type=="message") %>%
  filter(!is.na(text))

@@

### Utt Length (MLU)
```{r utt_length}

@@

ggplot(d_flowers_utt_length_block, aes(x=blockNum, y=total_num_words, color=condition))+
  #facet_grid(rows =vars(condition)) +
  geom_point()+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Total number of words", x="Block number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("Number of words per block")#+
 # theme(text = element_text(size = 30))
#color="gameId" cols = vars(blockNum),
#dev.off()

@@

ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=total_num_words,  color=condition))+
#  facet_grid(rows =vars(condition)) +
  geom_point()+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Total number of words", x="Trial number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("Number of words per trial")

ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=mlu,  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="Mean Length of Utterance", y="MLU", x="Trial number")+
  theme_jmank() + scale_color_bay() + theme(legend.position="bottom") #+ 
  #theme(text = element_text(size = 30))

@@

#jpeg("~/Desktop/plots/nword_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_rep, aes(x=repNum, y=log(mlu+1),  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Rep number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("MLU per rep")#+
 # theme(text = element_text(size = 30))
#dev.off()

### Number of turns
```{r number_of_turns}

@@

#ggsave("../figs/num_turns_block.png", height = 3, width = 3)
```

@@

@@

```{r number_of_turns3}

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(trialNum, blockNum, gameId, condition) %>%
  summarise(n_utt_speaker=n())

turnb_function <- function(d_flowers_n_utt_speaker, c, q) {
  p<-ggplot2::ggplot(d_flowers_n_utt_speaker, aes(y=n_utt_speaker, x=trialNum, label=gameId, color=condition)) + xlim(c,q) +
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", formula = y~x)+
  xlab("Trial number") + 
  theme_bw()+
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
return(p)
}

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
a<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==0), 0,5) + ylab("Number of utterances")+  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank())+ labs(subtitle = "Block1")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
b<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==1), 6,11) +  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block2")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
c<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==2), 12,17) +  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block3")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
d<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==3), 18,23) +theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block4")

legend <- get_legend(
  # create some space to the left of the legend
  d +  theme(legend.position = "right")
)

p<- plot_grid(a,b,c,d, legend,  nrow = 1, ncol=5, align = "v")

x.grob <- textGrob("Trial Number")
y.grob <- textGrob("Number of utterances", rot=90)
grid.arrange(arrangeGrob(p, left = y.grob, bottom = x.grob))

### Parts of speech
```{r pos, eval=TRUE, include=TRUE}

d_flowers_uttlength_nwords <- d_flowers %>%
  mutate(text = gsub('[[:punct:] ]+',' ',text)) %>%
  mutate(utt_length_words = sapply(strsplit(text, " "), length)) %>% 
  group_by(gameId, blockNum, trialNum, condition)  %>%
  summarise(total_num_words = sum(utt_length_words),
            mlu = mean(utt_length_words))

 text <- d_flowers$text
 parsed <- spacy_parse(text,pos=TRUE) %>%
   select(doc_id, pos) %>%
   group_by(doc_id) %>%
   mutate(pos = paste(pos, collapse=",")) %>%
   distinct()
#   
# d_flowers_pos  <- cbind(d_flowers, parsed) %>%
#   separate_rows(pos, convert = TRUE) %>%
#   group_by(condition, blockNum, gameId, pos) %>%
 #  filter(pos=="NOUN"| pos=="VERB") %>% #| pos=="ADJ"| pos=="ADP"| pos=="DET" | pos=="PRON") %>%
  # summarise(pos_count=n()) %>%
  # left_join(d_flowers_uttlength_block) %>%
  # mutate(prop_pos=pos_count/total_num_words)

# #jpeg("~/Desktop/plots/pos_block.jpg", width = 950, height = 950)
 #ggplot(d_flowers_pos, 
#        aes(x=blockNum, y=prop_pos, label=gameId,  color=condition)) + 
#   geom_smooth(method = "lm", formula = y~x) + 
#   geom_point(alpha=.1) +
#   facet_grid( cols=vars(pos)) +
#   xlab("Block number") + 
#   ylab("Proportion of pos") + 
#   theme_bw()#+
#  # theme(text = element_text(size = 30))
# #dev.off() 
## 
# d_flowers_pos  <- cbind(d_flowers, parsed) %>%
#   separate_rows(pos, convert = TRUE) %>%
#   group_by(condition, trialNum, gameId, pos) %>%
#   filter(pos=="NOUN"| pos=="VERB" ) %>% #| pos=="ADJ"| pos=="ADP"| pos=="DET" | pos=="PRON") %>%
#   summarise(pos_count=n()) %>%
#   left_join(d_flowers_utt_length_trial) %>%
#   mutate(prop_pos=pos_count/total_num_words)
#         
# #jpeg("~/Desktop/plots/pos_trial.jpg", width = 950, height = 950)
# ggplot(d_flowers_pos, 
#        aes(x=trialNum, y=prop_pos, label=gameId,  color=condition)) + 
#   geom_smooth(method = "lm", formula = y~x) + 
#   geom_point(alpha=.1) +
#   facet_grid( cols=vars(pos)) +
#   xlab("Trial number") + 
 #  ylab("Proportion of pos") + 
#   ylim(0,5)+
#   theme_bw()#+
   #theme(text = element_text(size = 30))
# #dev.off() 
#

text <- d_flowers$text
parsed <- spacy_parse(text,pos=TRUE) %>%
  select(doc_id, pos) %>%
  group_by(doc_id) %>%
  mutate(pos = paste(pos, collapse=",")) %>%
  distinct()

d_flowers_pos  <- cbind(d_flowers, parsed) %>%
  separate_rows(pos, convert = TRUE) %>%
  group_by(condition, blockNum, trialNum, gameId, pos) %>%
  filter(pos=="NOUN"| pos=="VERB" ) %>% # pos=="ADJ"| pos=="DET" | pos=="PRON"
  summarise(pos_count=n()) %>%
  left_join(d_flowers_uttlength_nwords) %>%
  mutate(prop_pos=pos_count/total_num_words)

#jpeg("~/Desktop/plots/pos_block.jpg", width = 950, height = 950)
pos_function <-function(d_flowers_pos, c,q){

ggplot(d_flowers_pos, 
       aes(x=trialNum, y=prop_pos, label=gameId, color=condition, linetype=pos)) + 
  geom_smooth(method = "lm", formula = y~x) + 
 # geom_point(alpha=.5) +
 # facet_grid(cols=vars(condition)) +
 # ylim(0,1)+
  xlim(c,q)+
  theme_bw() 
}

a<- pos_function(d_flowers_pos %>% filter(blockNum==0), 0,5) +  theme(legend.position="none", axis.title.y = element_blank(),axis.title.x = element_blank())+
   labs(subtitle = "Block1") + ylim(0.0, 0.4)
b<- pos_function(d_flowers_pos %>% filter(blockNum==1), 6,11) +  theme(legend.position="none", axis.title.y = element_blank(),axis.text.y = element_blank(), axis.title.x = element_blank())+
   labs(subtitle = "Block2")+ ylim(0.0, 0.4)
c<- pos_function(d_flowers_pos %>% filter(blockNum==2), 12,17) +  theme(legend.position="none", axis.title.y = element_blank(), axis.title.x = element_blank(),axis.text.y = element_blank())+
   labs(subtitle = "Block3")+ ylim(0.0, 0.4)
d<- pos_function(d_flowers_pos %>% filter(blockNum==3), 18,23) +  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank())+
   labs(subtitle = "Block4")+ ylim(0.0, 0.4)

legend <- get_legend(
  # create some space to the left of the legend
  d +  theme(legend.position = "right")
)

p<-plot_grid(a,b,c,d, legend, nrow = 1, ncol=5,  align = "v")
x.grob <- textGrob("Trial Number")
y.grob <- textGrob("Proportion Verbs, Nouns", rot=90)
grid.arrange(arrangeGrob(p, left = y.grob, bottom = x.grob))

### Lexical Diversity (TTR)

@@

@@

```{r ttr2}
d_flowers_text_trial <- d_flowers %>%
    group_by(gameId, trialNum, blockNum, condition) %>%
    mutate(text_block = paste0(text, collapse = " ")) %>%
    select(-c(text)) %>%
    distinct()

ttr_function <- function(d_flowers_ttr_trial, c, q) {
  p<-ggplot2::ggplot(d_flowers_ttr_trial, aes(y=ttr_, x=trialNum, label=gameId, color=condition)) + xlim(c,q) + ylim(0.5, 1.0)+
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", formula = y~x)+
  theme_bw()+
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
return(p)
}

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
a<- ttr_function(d_flowers_ttr_trial %>% filter(blockNum==0), 0,5) + ylab("Type token ration")+  theme(legend.position="none",  axis.title.x = element_blank(), axis.title.y = element_blank())+ labs(subtitle = "Block1")

b<- ttr_function(d_flowers_ttr_trial %>% filter(blockNum==1), 6,11) + theme(legend.position="none", axis.title.x = element_blank(), axis.title.y = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block2")+ylim(0.5, 1.0)

c<- ttr_function(d_flowers_ttr_trial %>% filter(blockNum==2), 12,17) + theme(legend.position="none", axis.title.x = element_blank(), axis.title.y = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block3")+ylim(0.5, 1.0)

d<- ttr_function(d_flowers_ttr_trial %>% filter(blockNum==3), 18,23) + labs(subtitle = "Block4")+ theme(legend.position="none", axis.title.x = element_blank(), axis.title.y = element_blank(),axis.text.y = element_blank())+ylim(0.5, 1.0)

legend <- get_legend(
  # create some space to the left of the legend
  d +  theme(legend.position = "right")
)

p<-plot_grid(a,b,c,d, legend, nrow = 1, ncol=5, align = "v")
#dev.off() 
x.grob <- textGrob("Trial Number")
y.grob <- textGrob("Type token ratio", rot=90)
p<- grid.arrange(arrangeGrob(p, left = y.grob, bottom = x.grob))

#ggsave(file="../figs/ttr.png", p)

### Distribution of speech across speakers
```{r word_length}

@@

```{r word_length2}
d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(playerId, trialNum, blockNum, gameId, condition) %>%
  summarise(n_utt_speaker=n())

d_flowers_n_utt_game <- d_flowers %>%
  group_by(trialNum, blockNum, gameId, condition) %>%
  summarise(n_utt_game=n())

@@

turn_per_plot_function <- function(d_flowers_n_utt_dist, overall_turns, c,q) {
  p<-ggplot2::ggplot(d_flowers_n_utt_dist, aes(y={{overall_turns}}, x=trialNum, label=playerId)) +
  geom_point(alpha = .5)+
  xlim(c,q) +
  facet_wrap(~condition)+
  geom_smooth(method = "lm", formula = y~x)+
  theme_bw()+
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),axis.title.y = element_blank(),axis.title.x = element_blank())
return(p)
}

#jpeg("~/Desktop/plots/proputts_trial_speaker.jpg", width = 950, height = 950)
a<-turn_per_plot_function(d_flowers_n_utt_dist %>% filter(blockNum==0), overall_turns, 0,5) + ylab("Proportion of turns")+ labs(subtitle = "Block1") + theme_bw() + theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank())

b<-turn_per_plot_function(d_flowers_n_utt_dist %>% filter(blockNum==1), overall_turns, 6,11) +  theme(legend.position="none", axis.text.y=element_blank(),axis.title.x = element_blank(),axis.title.y = element_blank())+ labs(subtitle = "Block2")+ theme_bw()

c<-turn_per_plot_function(d_flowers_n_utt_dist%>% filter(blockNum==2), overall_turns, 12,17) +  theme(legend.position="none", axis.title.y = element_blank(), axis.text.y=element_blank(), axis.title.x = element_blank())+ labs(subtitle = "Block3")+ theme_bw()

d<-turn_per_plot_function(d_flowers_n_utt_dist%>% filter(blockNum==3), overall_turns, 18,23) +  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(), axis.text.y=element_blank(), plot.tag.position = "topright")+ labs(subtitle = "Block4")+ theme_bw()

legend <- get_legend(
  # create some space to the left of the legend
  d +  theme(legend.position = "right")
)

p<-plot_grid(a,b,c,d,  nrow = 2, ncol=3,  legend, align = "v")

x.grob <- textGrob("Trial Number")
y.grob <- textGrob("Proportion of turns", rot=90)
grid.arrange(arrangeGrob(p, left = y.grob, bottom = x.grob))

@@

### Questions

@@

##

@@

```{r questions2}

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(trialNum, blockNum, gameId, condition) %>%
  summarise(n_utt_speaker=n())

d_flowers_q <- d_flowers %>% 
 mutate(sentence_type = ifelse(str_detect(text, "\\?"), 
                             "question",
                             "other")) %>%
 group_by(trialNum, blockNum, gameId, sentence_type) %>%
 summarise(n_sentence_Type=n()) %>%
 filter(sentence_type=="question") %>%
 left_join(d_flowers_n_utt_speaker) %>%
 mutate(prop_questions = n_sentence_Type/n_utt_speaker )

word_per_plot_function <- function(d_flowers, prop_words, c, q) {
  p<-ggplot2::ggplot(d_flowers, aes(y={{prop_words}}, x=trialNum, label=gameId, color=condition)) + ylim(0.0,0.20)+ xlim(c,q) +
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", formula = y~x)+
  theme_bw()+
  xlab("Trial number") + 
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
return(p)
}

#jpeg("~/Desktop/plots/propquestions_trial.jpg", width = 950, height = 950)
a<- word_per_plot_function(d_flowers_q %>% filter(blockNum==0), prop_questions, 0,5) + ylab("Proportion of questions")+  theme(legend.position="none", axis.title.x = element_blank(), axis.title.y = element_blank())+ labs(subtitle = "Block1")

b<-word_per_plot_function(d_flowers_q %>% filter(blockNum==1), prop_questions, 6,11) +  theme(legend.position="none", axis.title.y = element_blank(), axis.text.y=element_blank(), axis.title.x = element_blank())+ labs(subtitle = "Block2")

c<-word_per_plot_function(d_flowers_q%>% filter(blockNum==2), prop_questions, 12,17) +  theme(legend.position="none", axis.title.y = element_blank(), axis.text.y=element_blank(), axis.title.x = element_blank())+ labs(subtitle = "Block3")

d<-word_per_plot_function(d_flowers_q%>% filter(blockNum==3), prop_questions, 18,23) +  theme(legend.position="none",axis.title.y = element_blank(), axis.text.y=element_blank(),axis.title.x = element_blank(), plot.tag.position = "topright")+ labs(subtitle = "Block4")

legend <- get_legend(
  # create some space to the left of the legend
  d +  theme(legend.position = "right")
)

p<-plot_grid(a,b,c,d,  nrow = 1, ncol=5, legend, align = "v")
x.grob <- textGrob("Trial Number")
y.grob <- textGrob("Proportion of questions", rot=90)
grid.arrange(arrangeGrob(p, left = y.grob, bottom = x.grob))

### Feedback words (backchannel, hedge)
```{r feedback}

backchanneling<- c("mm", "okay", "uh-huh", "ok", "mm-hm", "uh", "um", "agree", "uhuh", "mmm", "wow", "great", "mm", "hm",  "ummm", "hmmmm", "huh", "un", "um", "ohh", "ooo", "see", "oooo", "ununun", "oh", "ah", "true", "agree", "right", "yeah", "good", "really") #backchanneling: (https://www.reading.ac.uk/AcaDepts/ll/app_ling/internal/Cutrone_vol_2.pdf)

hedging <- c("may", "perhaps", "might", "possible", "likely", "possibly", "maybe", "probable", "appear", "seem", "suggest", "sometimes", "seemingly", "apparently", "often", "could", "usually", "likely", "tend", "sometimes", "probably", "primarily", "tendency", "largely") #based on https://www.researchgate.net/publication/280125979_Linguistic_Markers_and_Stylistic_Attributes_of_Hedging_in_English_Academic_Papers_Written_by_Native_and_Non-Native_Speakers_of_English/figures

@@

@@

```{r feedback2}
